---
title: "Reproducibility Report: Group B Choice 3"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

------------------------------------------------------------------------

For this exercise, please try to reproduce the results from Experiment 2 of the associated paper (de la Fuente, Santiago, Roman, Dumitrache, & Casasanto, 2014). The PDF of the paper is included in the same folder as this Rmd file.

#### Methods summary:

Researchers tested the question of whether temporal focus differs between Moroccan and Spanish cultures, hypothesizing that Moroccans are more past-focused, whereas Spaniards are more future-focused. Two groups of participants ($N = 40$ Moroccan and $N=40$ Spanish) completed a temporal-focus questionnaire that contained questions about past-focused ("PAST") and future-focused ("FUTURE") topics. In response to each question, participants provided a rating on a 5-point Likert scale on which lower scores indicated less agreement and higher scores indicated greater agreement. The authors then performed a mixed-design ANOVA with agreement score as the dependent variable, group (Moroccan or Spanish, between-subjects) as the fixed-effects factor, and temporal focus (past or future, within-subjects) as the random effects factor. In addition, the authors performed unpaired two-sample t-tests to determine whether there was a significant difference between the two groups in agreement scores for PAST questions, and whether there was a significant difference in scores for FUTURE questions.

------------------------------------------------------------------------

#### Target outcomes:

Below is the specific result you will attempt to reproduce (quoted directly from the results section of Experiment 2):

> According to a mixed analysis of variance (ANOVA) with group (Spanish vs. Moroccan) as a between-subjects factor and temporal focus (past vs. future) as a within-subjectS factor, temporal focus differed significantly between Spaniards and Moroccans, as indicated by a significant interaction of temporal focus and group, F(1, 78) = 19.12, p = .001, ηp2 = .20 (Fig. 2). Moroccans showed greater agreement with past-focused statements than Spaniards did, t(78) = 4.04, p = .001, and Spaniards showed greater agreement with future-focused statements than Moroccans did, t(78) = −3.32, p = .001. (de la Fuente et al., 2014, p. 1685).

------------------------------------------------------------------------

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(rstatix)
# #optional packages/functions:
library(afex) # anova functions
library(ez) # anova functions 2
# library(scales) # for plotting
# std.err <- function(x) sd(x)/sqrt(length(x)) # standard error
```

# Step 2: Load data

```{r}
# Just Experiment 2
data_path <- 'data/DeLaFuenteEtAl_2014_RawData.xls'
d <- read_excel(data_path, sheet=3) %>% 
    rename(agreement = "Agreement (0=complete disagreement; 5=complete agreement)") %>% 
  group_by(group, participant) %>%             # group by group & participant
  mutate(participant_ID = cur_group_id()) %>%  # assign unique ID
  ungroup()

```

# Step 3: Tidy data

```{r}
participant_level <- d %>% 
  # group_by(group, participant) %>%             # group by group & participant
  # mutate(participant_ID = cur_group_id()) %>%  # assign unique ID
  # ungroup() %>% 
  group_by(participant_ID, group, subscale) %>% 
  summarize(mean_agreement = mean(agreement)) %>% 
  mutate(participant_ID=as.factor(participant_ID),
         group=as.factor(group),
         subscale=as.factor(subscale)) 
  

```

# Step 4: Run analysis

## Pre-processing

```{r}
aggregate_level <- d %>% 
  group_by(group, subscale) %>% 
  get_summary_stats(agreement, type = "mean_se")
  
```

## Descriptive statistics

Try to recreate Figure 2 (fig2.png, also included in the same folder as this Rmd file):

```{r}
fig2 <- aggregate_level %>% 
  mutate(group=case_when(group=="young Spaniard"~"Spaniards",
                         group=="Moroccan"~"Moroccans")) %>% 
  mutate(group=fct_relevel(group, c("Spaniards", "Moroccans")),
         subscale=fct_relevel(subscale, c("PAST", "FUTURE"))) %>% 
  ggplot(aes(x=group, y=mean, fill=subscale)) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                position=position_dodge2(width=.5, padding=.5)) +
  labs(y="Rating",
       x="") +
  coord_cartesian(ylim=c(2,4)) +
  theme(legend.title = element_blank())

fig2
  
```

## Inferential statistics

> According to a mixed analysis of variance (ANOVA) with group (Spanish vs. Moroccan) as a between-subjects factor and temporal focus (past vs. future) as a within-subjects factor, temporal focus differed significantly between Spaniards and Moroccans, as indicated by a significant interaction of temporal focus and group, F(1, 78) = 19.12, p = .001, ηp2 = .20 (Fig. 2).

```{r}
# reproduce the above results here


# Run mixed ANOVA
aov_result <- aov_ez(
  id = "participant_ID",        # subject identifier column
  dv = "mean_agreement",              # dependent variable
  between = "group",         # between-subjects factor
  within = "subscale",       # within-subjects factor
  data = participant_level
)

summary(aov_result)

# These were the missing participants. I tried to see how the results change when they are excluded
removed_missing <- participant_level %>% 
  filter(!participant_ID %in% c("25", "65"))


```

> Moroccans showed greater agreement with past-focused statements than Spaniards did, t(78) = 4.04, p = .001,

```{r}
# reproduce the above results here

# unpaired t-test comparing agreement scores for subscale = PAST

past <- participant_level %>% 
  filter(subscale=="PAST")

t.test(mean_agreement~group, var.equal=TRUE, data=past)

```

> and Spaniards showed greater agreement with future-focused statements than Moroccans did, t(78) = −3.32, p = .001.(de la Fuente et al., 2014, p. 1685)

```{r}
# reproduce the above results here
future <- participant_level %>% 
  filter(subscale=="FUTURE")

t.test(mean_agreement~group, var.equal=TRUE, data=future)
```

# Step 5: Reflection

Were you able to reproduce the results you attempted to reproduce? If not, what part(s) were you unable to reproduce?

> (Note: I stopped after reaching the three-hour time limit.) I wasn't able to reproduce the inferential statistics because of some missing data that was not accounted for in the paper. For example, for a couple participants they did not have data for BOTH future and past subscales, so I couldn't run the mixed ANOVA with the same denominator degrees of freedom. The paper reports denominator df = 78, but because two participants were missing data my denominator df = 76. Even for my second t-test, in which I compared future-focused statements and had the same df as the authors, I was not able to get the same test statistic. 


What aspects made it difficult? What aspects made it easy?

> Overall, the data was in a straightforward format with reasonable column names. I was able to reproduce the figure. However, the inferential statistics portion was difficult. There was not a unique participant ID that applied across the whole dataset so I had to create one for the analysis. Critically, data was missing for some participants and I didn't know how to account for that. The authors didn't report descriptive statistics within their reports of the main results, so it is hard to tell from where the discrepancy arose.
